Evolution of ORM Systems: Formal Foundations

### 2013-01-09 doc/description.tex
copy property defined

The copy property can be implemented as a transformation composed by operations for adding and removing property, nevertheless this composition would not work with instances, where the $copyData$ transformation is used.
\begin{align*}
	\mathbf{CopyProperty} : Label \times Label \times Label \times (Instance \times Instance) \times State \rightarrow State \\
	\Psi(CopyProperty(l_s, l_t, l_p, f_m), s) = \inference{\exists c \in classes(a) : name(c) = l_s \\ \wedge \exists p \in properties(c) : name(p) = l_p }{application(s) \circ addProp(l_t, p)} \\
	\Phi(CopyProperty(l_s, l_t, l_p, f_m), s) = \begin{cases}
		\inference{\mathbf{TODO}}{\begin{gathered}
			database(s) \bullet copyColumn(l_s, l_t, l_p) \\ \bullet copyValues(l_s, l_t, l_p, f_m) 
			\end{gathered}} \\ \\
		\inference{\mathbf{TODO}}{\begin{gathered}
			database(s) \bullet copyTable(l_s, l_t, l_p) \\ \bullet copyRows(l_s, l_t, l_p, f_m) 
			\end{gathered}}
 \end{cases}
\end{align*}

With a copy property transformation defined we are able to define advanced evolution scenarios.

>>>>

The copy property can be implemented as a transformation composed by operations for adding and removing property, nevertheless this composition would not work with instances, where the $copyData$ transformation is used.
\begin{align*}
	\mathbf{CopyProperty} : Label \times Label \times Label \times (Instance \times Instance) \times State \rightarrow State \\
	\Psi(CopyProperty(l_s, l_t, l_p, f_m), s) = \inference{\exists c \in classes(s) : name(c) = l_s \\ \wedge \exists p \in properties(c) : name(p) = l_p }{application(s) \circ addProp(l_t, p)} \\\\
	\Phi(CopyProperty(l_s, l_t, l_p, f_m), s) = \begin{cases}
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) \leq 1 }{\begin{gathered}
			database(s) \bullet copyColumn(l_s, l_t, l_p) \\ \bullet copyValues(l_s, l_t, l_p, f_m) 
			\end{gathered}} \\ \\
		\inference{\exists p \in properties(c), c \in classes(s) : \\ name(p) = l_p \wedge cardinality(p) > 1}{\begin{gathered}
			database(s) \bullet copyTable(l_s, l_t, l_p) \\ \bullet copyRows(l_s, l_t, l_p, f_m) 
			\end{gathered}}
 \end{cases}
\end{align*}

With the copy property transformation defined we are able to define advanced evolution scenarios.
